An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-04 EconGrowth2.Rnw
Added CD ternary plots.

Under that assumption, it would not be surprising if the residual from 
any one year had been observed on a different year. 
By applying randomly selected residuals (with randomly selected signs)
to model predictions at each year of the GDP time series, we create a resampled
GDP time series ($y_{resample,t}$) that can be fitted using the techniques
described below.

@@

The Cobb-Douglas model without energy is given by 
Equation~\ref{eq:CD}. The Cobb-Douglas (without energy) production function was
reparameterized as

@@

**** CD without energy results here. Scatter plots? CIs? 
Partial residual plots? TBD which to include. ****

@@

**** Include CD$e$ graphs here. Ternary plots? CIs? TBD which to include. ****

@@

<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
createCESLatticeGraph()
@

>>>>

Under that assumption, it would not be surprising if the residual from 
any one year had been observed in a different year. 
By applying randomly selected residuals (with randomly selected signs)
to model predictions at each year of the GDP time series, we create a resampled
GDP time series ($y_{resample,t}$) that can be fitted using the techniques
described below.

@@

The Cobb-Douglas model without energy is given by 
Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
reparameterized as

@@

Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
of $\alpha$, $\beta$, and $\gamma$ parameter values 
for resample models for the Cobb-Douglas model (without energy). 
In Figure~\ref{fig:CD_Scatter_Graph}, 
$\gamma$ is always 0.0, because energy is not included in this model.

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA)
@

Converting the resample data into 95\% confidence intervals 
provides data for Figure~\ref{fig:CD_Params_Graph}.
Appendix~\ref{sec:Model_Parameters} 
contains tables with numerical values of 
Cobb-Douglas model parameters and 95\% confidence intervals.

<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCDParamsGraph(energyType=NA)
@

@@

Figure~\ref{fig:CDq_Cloud_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (with energy) resample models.

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.", eval=FALSE>>=
createCESLatticeGraph()
@
